\documentclass{article}
\usepackage{amsmath}

\begin{document}

\subsection*{1}

The algorithm creates two rdds. 
The first rdd has tuples of direct nodes as keys and None as values, 
and the second rdd has tuples of indirect nodes as keys and the node in between as values.
To this end, the algorithm parses the given file as follows:

\[
1 \quad 2,3,4 \rightarrow (1, 2): None, (1, 3): None, (1, 4): None
\]
\[
1 \quad 2,3,4 \rightarrow (2, 3): [1], (2, 4): [1], (3, 4): [1]
\]

\noindent
The first rdd is subtracted from the second rdd to leave only indirect nodes.
Then, the second rdd is reduced by key to get full lists of indirect nodes.
The resulting rdd counts the number of unique indirect nodes for each pair, 
and sorted by the desired order to get the final results.\newline

\noindent
The program's elapsed time is 3 min 58 sec on eelabg2 machine.

\subsection*{2-(a)}
For the first pass, both algorithms require an integer array of length 1 million 
to count the occurences of each item.
For the second pass of the triangular-matrix method requires an integer array of size
\(\frac{N(N-1)}{2}\)
Hence, the minimum number of bytes of main memory for triangular-matrix is \(4*10^6 + 4*\frac{N(N-1)}{2}\) bytes.
For the second pass of the hash table method, 1 million pairs above threshold are stored.
In addition, for pairs that appear exactly once, and of those pairs, the ones that are both frequent items are stored.
Hence, the minimum number of bytes of main memory for hash table is \(4*10^6 + 12*(10^6 + M)\) bytes.

\subsection*{2-(b)}
The program's elapsed time is 22.62 sec on eelabg2 machine.

\subsection*{2-(c)}
The program's elapsed time is 6.33 sec on eelabg2 machine.

\subsection*{3-(a)}
Suppose the probability of two elements being equal is \(p\), then \newline


\noindent (a): The probability becomes \(1-(1-p^2)^3\)

\noindent (b): The probability becomes \((1-(1-p)^3)^2\)

\noindent (c): The probability becomes \((1-(1-p^2)^2)^2\)

\noindent (d): The probability becomes \( (1-(1-(1-(1-p)^2)^2)^2)^2 \)

\subsection*{3-(b)}
The program's elapsed time is 59.10 sec on eelabg2 machine.

\end{document}